A Partitioning Algorithm for Maximum Common Subgraph Problems

### 2017-02-17 paper/paper.tex
Quickie heuristics

?? Reword for here, explain later Small scale experiments (not presented here)
were performed to identify a suitable heuristic for label class selection. The
heuristic used selects the label class  with the smallest $\min(|\setG|,|\setH|)$ (a
surrogate for expected branching factor). From this class, a vertex is selected
from $\setG$ with maximum degree if $\graphH$ is sparse and with minimum degree if $\graphH$ is
dense.

>>>>

Small scale experiments (not presented here) were performed to identify
suitable heuristics for selecting a label class abd a vertex within a label
class selection. Our heuristic of choice selects the label class with the
smallest $\min(|\setG|,|\setH|)$. From this class, a vertex is selected from
$\setG$ with maximum degree if $\graphH$ is sparse and with minimum degree if
$\graphH$ is dense. We discuss this further in \cref{sec:comparison}.
